Relative Photometry of HD 227858 and HD 338931 from Landholt Standard SA 113475

### 2013-12-10 paper.tex
COEFFICIENT

\section{Analysis}
$S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
\begin{tabular}{c | c | c | c | c}
Star & Filter & X & $S_{*,sky}$ & $S_{sky}$ \\
\hline
HD 227858 & B & & 668721.3 & 1088003.27\\
HD 227858 & I & & 503371.8 & 427838.5534\\
HD 227858 & R & & 669765.3 & 1028251.386\\
HD 227858 & V & & 396151.3 & 700931.7268\\
HD 338931 & B & & 1118167 & 463203.7293\\
HD 338931 & I & & 1021443 & 422439.6612\\
HD 338931 & R & & 1062403 & 1035817.766\\
HD 338931 & V & & 567930 & 708921.9555\\
SA 113475 & B & & 139874.2 & 479501.2852\\
SA 113475 & I & & 461871.4 & 678267.3456\\
SA 113475 & R & & 643029.1 & 1699412.832\\
SA 113475 & V & & 367109.7 & 1110109.973\\
SA 113475 & B & & 565539.5 & 1492937.888\\
SA 113475 & I & & 1992206 & 4536981.855\\
SA 113475 & R & & 250266.8 & 626392.1272\\
SA 113475 & V & & 318196.8 & 983429.69\\
\end{tabular}

>>>>

\begin{center}
\begin{tabular}{c | c | c | c | c | c }
							%SUM              FLUX
Star & Filter & t(s) & $X=\sec{z}$ & $S_{*,sky}=\mathsf{SUM}$ & $S_*=\mathsf{FLUX=SUM-MSKY*AREA}$\\
\hline
HD 227858 & B & 30 & 1.294 & 117809 & 39381 \\
HD 227858 & V & 30 & 1.301 & 388133 & 131079  \\
HD 227858 & R & 30 & 1.307 & 567655 & 254168  \\
HD 227858 & I &  30 & 1.323 & 417430 & 260971   \\

HD 338931 & B & 30 & 1.394 & 255793 & 152570 \\
HD 338931 & V & 30 & 1.405 & 767017 & 494401  \\
HD 338931 & R & 30 & 1.413 & 1390626 &  977589 \\
HD 338931 & I & 30 &  1.424 & 1285304 &  1075136 \\

SA 113475 & B & 30 & 1.206  & 169993 & 38822  \\
SA 113475 & B & 30 & 1.482  & 179149 &  33471 \\

SA 113475 & V & 30 & 1.207  & 477466 & 154874 \\
SA 113475 & V & 30 & 1.498  & 665531 &  147737 \\

SA 113475 & R & 30 & 1.209 & 802783  & 344417  \\
SA 113475 & R & 30 & 1.498 & 1064716 & 332641 \\

SA 113475 & I & 30 & 1.213 & 477466  & 154874  \\
SA 113475 & I & 30 & 1.521& 665531 & 147737   \\

\end{tabular}
\end{center}

From \ref{eq:ext} and reference data for SA 113475, we arrive at the extinction coefficients:
\begin{align*}
k_B&= 0.583\\
k_V&= 0.176\\
k_R&= 0.131\\
k_I&= 0.166
\end{align*}
\begin{equation}
\label{eq:ext}
m_1-m_2=k(X_1-X_2)=-2.5\log_{10}\frac{S_1t_2}{S_2t_1}
\end{equation}
\section{Analysis}
$S_{*,sky}=\Delta\nu{\obar{\Phi}}{\obar{f}}tA/g$
